Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-07-05 PAPER/main.tex
added statement about combinatorial explosion, changed figure size

Clearly, for two items to be placed alongside one another feasibly, the distance between the two score lines from adjacent items must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations. Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance\footnote{Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.}. It follows that there are $\frac{n!}{2}$ $2^n$ distinct arrangements of items, and so as $n$ increases,

@@

\begin{figure}	
	\centering
	\begin{subfigure}[t]{0.4\textwidth}
		\includestandalone[width=\textwidth]{figures/matching}
		\caption{$G' = (V, B \cup R')$}	
		\label{fig:matching}
	\end{subfigure} \quad
	\begin{subfigure}[t]{0.55\textwidth}
		\includestandalone[width=\textwidth]{figures/mps}
		\caption{Planar representation of $G' =(V, B \cup R')$}	
		\label{fig:mps}
	\end{subfigure}
	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MCM. The same solution is shown in planar form in (b).}
	\label{fig:matching/mps}
\end{figure}

@@

\begin{theorem}
	\label{thm:copsoln}
	If there exists an alternating Hamiltonian cycle on a graph $G$ created from an instance $\mathcal{M}$ of the COP, then AHC is able to find the cycle in $O(n^2)$ time.
\end{theorem}
\begin{proof}
	\begin{itemize}
		\item Initial creation of $G = (V, B \cup R)$ - $O(n^2)$.
		\item \textsc{Maximum Cardinality Matching} - $O(n\log n)$ due to initial sorting of vertices.
		\item \textsc{Bridge Recognition}:
		\begin{itemize}
			\item sort edges into list and remove invalid egdes - $O(n \log n)$.
			\item go through list to put into sets $R_i$, each edge assessed exactly once - $O(n)$.
			\item check every set $R_i$ to see if $|R_i| = q$, since there must be a minimum of two red/matching edges in a set $R_i$, there can be at most $\frac{n}{2}$ $R_i$ sets created - $O(n)$.
			\item check overlapping/multiple sets - ?
		\end{itemize}	
		\item Connecting Procedure - $n+1$ red edges on $G'$, so maximum every red edge in $R'$ needs to be replaced, $n+1$ edges to replace with edges from sets $R_i$. so at most $n+1$ edges need to be added to $G'$ and $n+1$ edges removed (edges added to $R'$ and removed from $R'$) - $O(n)$.
	\end{itemize}
	Hence complexity of AHC is $O(n^2)$ time.
	\qed
\end{proof}

@@

That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the vicinal sum constraint is fulfilled, that is, the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance $\tau$ (\ref{eqn:vscstrip}). Note that equations \ref{eqn:packall} - \ref{eqn:capacity} are the necessary conditions for the BPP.

@@

\section{Conclusions and Further Work}
\begin{itemize}
	\item This paper introduced a SPP with score constraints, where the order and orientation of the items is crucial to the feasibility of the solution (for example).
	\item We showed that a solution can be found for the single strip version of the problem (subproblem) in p-time/ we showed an exact p-time alg for the single strip version of the problem. 
	\item exact p-time alg for COP used to solve subproblem
	\item Thus the main problem was finding solutions for the multistrip version
	\item Created 3 heuristics, one which included the p-time alg. 
	\item shown how AHC can be combined with well known heuristic to produce a method for tackling multistrip version of the problem, the SCSPP.
	\item Experimental results show that ...
	\item Further work.
	\item items closer to practical applications, multiple items having same width and score widths
	\item Genetic algorithm/EA
	\item Operating theatre cleaning/scheduling
	\item lower bound for the optimal number of strips SCSPP
	\item \cite{miller1960} TSP returning to base
	\item mffd+ items are packed one by one, could be a case where an items fits onto a strip but ahc cannot find a feasible solution, so item must be packed elsewhere, but if two new items could fit on the strip, ahc might be able to find a solution. 
	\item include item width in ahc, so add values to the blue edges of the graph, weighted edges, red edges have value = 0.
	\item Then the problem would be: find the minimum number of alternating cycles on $G$ such that the length of the cycle is less than or equal to some value $W$ (which is the strip width). The length of the cycle would be the sum of all the weighted edges, so the sum of all the blue edges, since red = 0. 
	\item then could break and form edges to create new components of different sizes if some are too large, or join together if some are small, thus decreasing the number of cycles
	\item or if possible, find a single alt Ham cycle, and break up into as few smaller cycles as possible such that the length of each cycle is less than or equal to $W$
	\item another way, create as few feasible subsets $\mathcal{I}' \subseteq \mathcal{I}$ such that the total width of the items in each subset $\mathcal{I}$ is less than $W$, i.e. perform usual FFD alg, ignore score widths
	\item then perform ahc on each set, try to find feasible solution.
	\item if sets dont have feasible solution, try swapping items between sets
	\item initial tests, Becker theorem 6 2015 paper \cite{garraffa2016}
	\item minimise waste on each strip, not just number of strips
	\item tsp return to base
\end{itemize}

>>>>

Clearly, for two items to be placed alongside one another feasibly, the distance between the two score lines from adjacent items must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations. Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance\footnote{Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.}. It follows that there are $\frac{n!}{2}2^n$ distinct arrangements of items, and so complete enumeration can cause a combinatorial explosion.

@@

\begin{figure}	
	\centering
	\begin{subfigure}[t]{0.4\textwidth}
		\includestandalone[width=\textwidth]{figures/matching}
		\caption{$G' = (V, B \cup R')$}	
		\label{fig:matching}
	\end{subfigure} \quad
	\begin{subfigure}[t]{0.57\textwidth}
		\includestandalone[width=\textwidth]{figures/mps}
		\caption{Planar representation of $G' =(V, B \cup R')$}	
		\label{fig:mps}
	\end{subfigure}
	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MCM. The same solution is shown in planar form in (b).}
	\label{fig:matching/mps}
\end{figure}

@@

\begin{theorem}
	\label{thm:copsoln}
	If there exists an alternating Hamiltonian cycle on a graph $G$ created from an instance $\mathcal{M}$ of the COP, then AHC is able to find the cycle in at most $O(n^2)$ time.
\end{theorem}
\begin{proof}
	\begin{itemize}
		\item Initial creation of $G = (V, B \cup R)$ - $O(n^2)$.
		\item \textsc{Maximum Cardinality Matching} - $O(n\log n)$ due to initial sorting of vertices.
		\item \textsc{Bridge Recognition}:
		\begin{itemize}
			\item sort edges into list and remove invalid egdes - $O(n \log n)$.
			\item go through list to put into sets $R_i$, each edge assessed exactly once - $O(n)$.
			\item check every set $R_i$ to see if $|R_i| = q$, since there must be a minimum of two red/matching edges in a set $R_i$, there can be at most $\frac{n}{2}$ $R_i$ sets created - $O(n)$.
			\item check overlapping/multiple sets - ?
		\end{itemize}	
		\item Connecting Procedure - $n+1$ red edges on $G'$, so maximum every red edge in $R'$ needs to be replaced, $n+1$ edges to replace with edges from sets $R_i$. so at most $n+1$ edges need to be added to $G'$ and $n+1$ edges removed (edges added to $R'$ and removed from $R'$) - $O(n)$.
	\end{itemize}
	Hence complexity of AHC is $O(n^2)$ time.
	\qed
\end{proof}

@@

That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the vicinal sum constraint is fulfilled, that is, the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance $\tau$ (\ref{eqn:vscstrip}). Note that equations (\ref{eqn:packall}) - (\ref{eqn:capacity}) are the necessary conditions for the BPP.

@@

\section{Conclusions and Further Work}
\begin{itemize}
	\item This paper introduced a SPP with score constraints, where the order and orientation of the items is crucial to the feasibility of the solution (for example).
	\item We showed that a solution can be found for the single strip version of the problem (subproblem) in p-time/ we showed an exact p-time alg for the single strip version of the problem. 
	\item exact p-time alg for COP used to solve subproblem
	\item Thus the main problem was finding solutions for the multistrip version
	\item Created 3 heuristics, one which included the p-time alg. 
	\item shown how AHC can be combined with well known heuristic to produce a method for tackling multistrip version of the problem, the SCSPP.
	\item Experimental results show that ...
	\item Further work.
	\item items closer to practical applications, multiple items having same width and score widths
	\item Genetic algorithm/EA
	\item Operating theatre cleaning/scheduling
	\item lower bound for the optimal number of strips SCSPP
	\item \cite{miller1960} TSP returning to base
	\item mffd+ items are packed one by one, could be a case where an items fits onto a strip but ahc cannot find a feasible solution, so item must be packed elsewhere, but if two new items could fit on the strip, ahc might be able to find a solution. 
	\item include item width in ahc, so add values to the blue edges of the graph, weighted edges, red edges have value = 0.
	\item Then the problem would be: find the minimum number of alternating cycles on $G$ such that the length of the cycle is less than or equal to some value $W$ (which is the strip width). The length of the cycle would be the sum of all the weighted edges, so the sum of all the blue edges, since red = 0. 
	\item then could break and form edges to create new components of different sizes if some are too large, or join together if some are small, thus decreasing the number of cycles
	\item or if possible, find a single alt Ham cycle, and break up into as few smaller cycles as possible such that the length of each cycle is less than or equal to $W$
	\item another way, create as few feasible subsets $\mathcal{I}' \subseteq \mathcal{I}$ such that the total width of the items in each subset $\mathcal{I}$ is less than $W$, i.e. perform usual FFD alg, ignore score widths
	\item then perform ahc on each set, try to find feasible solution.
	\item if sets dont have feasible solution, try swapping items between sets
	\item initial tests, Becker theorem 6 2015 paper \cite{garraffa2016}
	\item minimise waste on each strip, not just number of strips
\end{itemize}
